Computer Science House By-Laws

### 2017-06-24 bylaws.tex
Fixed periods and capitalization

	\item The applicant submits an application to the Evaluations Director for review
	\item The applicant participates in an informal interview with exactly three current Active, Alumni, or Honorary Members
	\item The application materials are then reviewed at an Evaluations meeting

>>>>

	\item The applicant submits an application to the Evaluations Director for review.
	\item The applicant participates in an informal interview with exactly three current Active, Alumni, or Honorary Members.
	\item The application materials are then reviewed at an Evaluations meeting.
